---
title: "Research Data Management Training"
knitr:
  opts_knit: 
    message: false
execute: 
  echo: false
  warning: false
---

All PhD candidates who started after January, 2020, are required to attend some form of Data Management training. 
There are two training options for PhD candidates at Mechanical Engineering:

1. <a href="./#course-description">RDM Training for ME PhD students</a> – ME Graduate School Course
    - Regularly delivered by the Data Steward to cover all ME PhD students
    - 5.5 - 7 h (depending on collection of personal data) divided into 3 Parts over 6 – 9 months
    - 1 GS

2. <a href="https://www.tudelft.nl/en/library/research-data-management/r/training-events/training-for-researchers/research-data-management-101">Research Data Management 101</a> - Central Graduate School Course
    - Delivered 4 times a year by the TU Delft Library
    - 16 hours divided in 3 weeks
    - 1.5 GS

For more information about option 2, visit the [website](https://www.tudelft.nl/en/library/research-data-management/r/training-events/training-for-researchers/research-data-management-101)
or contact [RDMtraining-lib@tudelft.nl](mailto:RDMtraining-lib@tudelft.nl).

## RDM Training at ME

This course is offered by the ME Graduate School to support PhD candidates at the ME faculty with the Research Data Mangement [policy](https://d2k0ddhflgrk1i.cloudfront.net/Library/Themaportalen/RDM/Beleid/2020_3mE_Research_Data_Management_Policy.pdf) requirements. The course consists of lectures with recommendations for data storage, project organisation, and data sharing and archiving. There will also be a practical component where students will get hands-on experience developing a Data Management Plan (DMP) using the [DMPonline](https://dmponline.tudelft.nl) platform.

For more information about the course, and for registration, contact {{< var instructor.name >}} at {{< var instructor.email >}}.

## Upcoming schedule

### Part 1

```{r}
#| label: setup
#| include: false
library(dplyr)
library(readr)
library(lubridate)
schedule <- read_csv("training-sessions.csv")
```

```{r}
#| label: part1-schedule
schedule_part1 <- schedule %>%
    mutate(Date = as_date(Date)) %>%
    filter(Date > Sys.Date(),
        Session == "Part 1",
        Status != "Cancelled") %>%
    select(!c(Session, Status))

if(nrow(schedule_part1) == 0){
    cat("**TBD**")
} else {
    schedule_part1 %>%
        knitr::kable()
}
```

### Part 3

Registration for sessions is available on [Brightspace]({{< var brightspace.part3 >}}) for those who have completed parts 1 and 2.

```{r}
#| label: part3-schedule

schedule_part3 <- schedule %>%
    mutate(Date = as_date(Date)) %>%
    filter(Date > Sys.Date(),
        Session == "Part 3",
        Status != "Cancelled") %>%
    select(!c(Session, Status)) 

if(nrow(schedule_part3) == 0){
    cat("**TBD**")
} else {
    schedule_part3 %>%
        knitr::kable()
}
```

## Training outcomes

At the end of the course, you should be familiar with:

- The importance of proper data...
    + management
    + storage
    + documentation
- Developing your own DMP
- Personal data considerations

## Important info

The course will take 5.5 - 7 h (depending if your DMP includes collection of personal data)
divided into three parts over 6 – 9 months.

You will receive 1 GS for completing the training.

Certificates will be provided after the sessions, and can be uploaded to [DMA](https://dma.tudelft.nl) (You can choose any of the three categories in DMA).

If you need to submit your PhD agreement before following one of these trainings, under the section Other Arrangements – Data Management Plan, depending on the training you will follow, you can indicate one of the following:

1. Data Management Plan Training for 3mE PhD students
    - You are going to follow Data Management Plan Training for 3mE PhD students delivered by the faculty data steward within the first year of the PhD.
    - During this training, you will create a DMP in DMPonline and consult the faculty data steward.
    - After the training, you will discuss your DMP with your PhD supervisor(s).  
    - You will include your DMP in the Go/No Go Decision. 
2. Research Data Management 101
    - You are going to follow Research Data Management 101 delivered by the TU Delft Library within the first year of the PhD. 
    - During this training, you will create a DMP in DMPonline and consult the trainers, and the faculty data steward if needed.
    - After the training, you will discuss your DMP with your PhD supervisor(s).  
    - You will include your DMP in the Go/No Go Decision. 

It is the responsibility of the PhD supervisor(s) to approve the DMP, not the Data Steward.
A guide for the PhD supervisors can be found [here](https://d2k0ddhflgrk1i.cloudfront.net/Library/Themaportalen/RDM/5%20Things%20to%20check%20when%20looking%20at%20Data%20Management%20Plans%20%28DMPs%29%20-%20guidance%20for%20supervisors%20-%20FINAL%20VERSION%20%281%29.pdf).


## Important links

- [DMPonline (TU Delft)](https://dmponline.tudelft.nl)
- Brightspace module for Part 1 (under construction)
- [Brightspace module for Part 3]({{< var brightspace.part3 >}})
- [ME faculty policy for data management](https://filelist.tudelft.nl/Library/Themaportalen/RDM/Beleid/2020_3mE_Research_Data_Management_Policy.pdf)
